\Large \bf Climate Change Awareness and Willingness to Pay for its Mitigation: \\ Evidence from the UK

### 2018-11-14 writing/draft1/manuscriptAll.tex
adding

\date{\normalsize{September 2018}}
\title{\Large \bf What Does the Weather Say about Yields in Kenya}
\author{Monika Novackova and Pedram Rowhani and Martin Todd}
\affil{\small{Department of Geography, University of Sussex, Falmer, UK}}

@@

\FloatBarrier
\section{Methodology}\label{Method}

@@

\FloatBarrier
\section{Data}\label{Data}
All data used in this study except of predicted income and population density, which we use in robustness tests,  were collected in the survey conducted by \cite{SurveyUK}.

@@

\FloatBarrier

>>>>

\date{\normalsize{December 2017}}
\title{\Large \bf Climate Change Awareness and Willingness to Pay for its Mitigation: \\ Evidence from the UK}
\author{Monika Novackova and Richard Tol}
\affil{\small{Department of Economics, University of Sussex, Falmer, UK}}

@@

\FloatBarrier
\section{Econometric Methodology}\label{Method}

@@

\FloatBarrier
\section{Data and Survey Methodology}\label{Data}
All data used in this study except of predicted income and population density, which we use in robustness tests,  were collected in the survey conducted by \cite{SurveyUK}.

@@

\FloatBarrier
\section{Robustness}\label{Robust}

One of the important objectives of this study is to examine effects of behavioural variables on climate knowledge and climate change perception. Except of inequity aversion, none of the behavioural variables was chosen by lasso into any of our models. In spite of this, for each dependent variable we estimate a jackknife OLS with all the behavioural measures included as explanatory variables (besides the predictors selected by lasso) as robustness tests and to investigate possible changes in signs and significance levels of the previously
selected predictors.  We also add some other potentially confounding variables including population density, climate variables other than the dependent variable, degree of agreement with income redistribution, net assets and predicted income as an alternative to the income recorded in our survey~\citep{SurveyUK} since the income obtained from the survey is categorical rather than continuous. \footnote{We include these variables in the robustness tests although they were not originally chosen by lasso.}

The population density serves as a proxy for rural-urban classification. We include it in the robustness tests because we believe that whether one lives in rural or urban area can have considerable impact on attitudes towards climate change.

In each model we include attitude towards income redistribution as an indicator of political and ideological world-views as the ideological opinions were found to be especially important for explaining of attitudes towards climate change and measures of climate knowledge by large number of previous studies (e.g. \citet{Hamilton2011}, \citet{Kahan2012}, \citet{Kellstedt2008}).

Controlling for income and net assets is especially important for WTP as both income and assets are very likely to be correlated with WTP. However, also other variables, such as discount rates, can be correlated with income and net assets. Therefore, we examine whether controlling for them changes our estimates. As an alternative measure of income we use a prediction obtained from a regression model estimated using the ASHE data.

We noticed that the relationship between discount rate and each dependent variable exhibit similar, characteristic patterns. The values of dependent variables tend to be high for small values of discount rate, they are quite low for medium values of discount rate and they increase again for relatively high values of discount rate. Because of this parabolic shape, we include both linear and quadratic terms of discount rate as explanatory variables. The estimates of all coefficients are almost the same if the squared discount rate is omitted, but we only present the results of the models with both linear and quadratic term to keep the length of our paper within reasonable limit.

The descriptive statistics of the additional explanatory variables can be found in Table~\ref{Descriptive} in Appendix~$3$.

For WTP models we also perform other robustness tests.

\subsection{Climate change knowledge}\label{RobKnow}

In this section we estimate the climate knowledge model specified in Section~\ref{ResKnow} including the behavioural variables and additional potential confounders as discussed at the beginning of this Section~\ref{Robust}. The estimates are summarised in Table~\ref{ClimKnowInOut}. As we can see, all additional covariates and behavioural variables with except for climate seriousness perception and climate versus policy perception are insignificant.

Climate seriousness perception and climate versus policy perception are negative and strongly significant predictors of climate knowledge (see Table~\ref{ClimKnowInOut}). This is not surprising given the fact that climate knowledge is negative and significant when included as an explanatory variable for both of these climate concern variables (see Tables~\ref{Climcare435} and~\ref{Climpol435} in Section~\ref{ResPerc}). There are two possible explanations. $(i)$ Individuals, who are less educated in climate change tend to believe to incorrect statements and mechanisms which would imply that climate change is much more serious than it actually is \citep{reynolds2010now, WhatPplKnow94}. In this case, the direction of dependency would be the other way around. $(ii)$ The negative correlation is caused by affective orientation towards global warming \citep{Kahan2015}. That is, people who believe in anthropogenic climate change and correctly assert, for example, that usage of fossil fuels is one of the causes of global warming are also likely to affirm other, perhaps false propositions which would imply higher environmental risks, for example that atmospheric emissions of sulphur contribute to global warming \citep{reynolds2010now}.

The estimates of the predictors which were originally chosen by the multisplit lasso are qualitatively the same as those in Section~\ref{ResKnow} (see Table~\ref{Know435}). The estimates are robust.
\caption{\vspace{-0.2cm}\textit{\textbf{Climate change knowledge:} Jackknife OLS - robustness}}
% soubor Know435InOut.R  Know535InOutKm2.R 
\label{ClimKnowInOut} 
\vspace{-1.35cm}
 \hline \vspace{-0.3cm}
% ResKnmow435io
\vspace{-0.33cm}Gender = male&$0.280$&$1\times10^{-8}~^{***}$&$0.282$&$<2\times10^{-8}~^{***}$\\
\vspace{-0.33cm}Cognitive reflection $=0.5$&$0.863$&$1.000$&$0.934$&$1.000$\\
  \vspace{-0.33cm}Cognitive reflection $=1$&$0.107$&$1.000$ &$0.112$&$1.000$\\
  \vspace{-0.33cm}Cognitive reflection $=1.5$&$0.432$&$1.000$&$0.461$&$1.000$\\
\vspace{-0.33cm}Cognitive reflection $=2$&$0.258$&$0.001~^{**}$&$0.255$&$0.003~^{**}$\\
  \vspace{-0.33cm}Cognitive reflection $=2.5$&$0.520$&$1.000$ &$0.537$&$1.000$\\
 Cognitive reflection $=3$&$0.450$&$1\times10^{-7}~^{***}$&$0.448$&$5\times10^{-7}~^{***}$\\
\hline \vspace{-0.33cm}
\vspace{-0.33cm}Income - predicted (mill. \textsterling~/yr.)&$-0.273$&$1.000$&\multicolumn{2}{c}{\textit{Not included}}\\ %income PREDICTED!!
\vspace{-0.33cm}Income - reported (mill. \textsterling~/yr.)\tnote{a}&\multicolumn{2}{c}{\textit{Not included}}&\textit{varies}&$1.000$\\ %income PREDICTED!!
\vspace{-0.33cm}Net assets (mill. \textsterling)&$0.026$&$1.000$&$0.020$&$1.000$\\ 
\vspace{-0.33cm}People per mill. km\textsuperscript{2}-LSOA level&\multirow{1}{*}{$1.416$}&\multirow{1}{*}{$1.000$}&\multicolumn{2}{c}{\multirow{1}{*}{\textit{Not included}}}\\%ha is a symbol for hectares
\vspace{-0.33cm}People per mill. km\textsuperscript{2}-LAD level&\multicolumn{2}{c}{\multirow{1}{*}{\textit{Not included}}}&\multirow{1}{*}{$0.254$}&\multirow{1}{*}{$1.000$}\\%ha is a symbol for hectares
  \vspace{-0.33cm}WTP-gas and electricity tax (\textsterling~/ yr.)&$-0.0003$&$1.000$&$-0.0001$&$1.000$\\
  \vspace{-0.33cm}WTP-duty on transport fuel (pence/ yr.)&$0.001$&$1.000$&$0.0006$&$1.000$\\
    \vspace{-0.33cm}Climate seriousness perception&$-0.077$&$<2\times10^{-8}~^{***}$&$-0.076$&$<2\times10^{-8}~^{***}$\\
    \vspace{-0.33cm}Climate vs. policy effects perception&$-0.043$&$0.0009~^{***}$&$-0.044$&$0.001~^{**}$\\
\vspace{-0.33cm}Social value orientation (ring meas.)&\multirow{1}{*}{$0.0008$}&\multirow{1}{*}{$1.000$}&\multirow{1}{*}{$0.0007$}&\multirow{1}{*}{$1.000$}\\
  \\ \vspace{-0.33cm}\multirow{1}{*}{Inequity aversion (categorical)}&\textit{varies}& \multirow{1}{*}{$1.000$}& \multirow{1}{*}{\textit{varies}}& \multirow{1}{*}{$1.000$}\\      
    \\ \vspace{-0.33cm}Discount rate yr. from now&$-0.001$&$1.000$&$-0.001$&$1.000$\\  
 \vspace{-0.33cm}Discount rate yr. from now - sq.\tnote{b}&\multirow{1}{*}{$2\times10^{-6}$}&\multirow{1}{*}{$1.000$}&\multirow{1}{*}{$2\times10^{-6}$}&\multirow{1}{*}{$1.000$}\\
  \\  \vspace{-0.33cm}Risk aversion coefficient\tnote{c}&\multicolumn{2}{c}{\textit{Not included}}&$-0.390$&$1.000$\\          
Redistribution of income (cat.)\tnote{d}&$-$,\textit{varies}&$1.000$&$-$,\textit{varies}&$1.000$\\
     Mean adjusted \textit{R\textsuperscript2}:&\multicolumn{2}{c}{$0.071$}&\multicolumn{2}{c}{$0.072$}\\
 \item[a]~Self reported income is only available as categorical.
\item[b]~If squared discount rate is omitted, linear discount rate remains insignificant and the estimates of the other covariates are almost the same as those presented in this table.

\subsection{Climate change risk perception}\label{RobPerc}

In this section we discuss robustness of the climate risk perception models. The models which were specified using lasso in Section~\ref{ResPerc} are re-estimated with behavioural variables and additional potential confounders among explanatory variables. The estimates of the climate seriousness perception models are summarised in Table~\ref{ClimCareInOut} and the estimates of the models for climate change versus policy perception can be found in Table~\ref{ClimPolInOut}.

As apparent from Table~\ref{ClimCareInOut}, all the behavioural variables and the additional potential confounders are insignificant for climate seriousness, with exemption of the climate variables. The significance of the climate variables is in accordance with our expectation and it confirms that our climate measures are valid. The estimates of the predictors selected using lasso are qualitatively equivalent to the estimates in Table~\ref{Climcare435}, hence our results are robust.

Table~\ref{ClimPolInOut} summarises the estimates of models with climate change versus policy as a dependent variable. Alike in the case of the climate seriousness model, all the behavioural variables, income, assets and population density are insignificant while the climate variables are significant. This is what we expected for the climate measures to be valid. However, understanding of inflation is not significant in Table~\ref{ClimPolInOut} while it is strongly significant in the model specified using lasso (see Table~\ref{Climpol435}). This is probably a result of the mediation relationship structure among climate versus policy, financial literacy and WTP discussed in Section~\ref{ResWTP}. Level of understanding of inflation is correlated with WTP. If we remove WTP for gas and electricity and WTP for transport fuel keeping all other variables in, understanding of inflation becomes significant. Estimates of this variety can be found in Table~\ref{ClimPolIOnoWTP} in Appendix~$3$. This evidence is consistence with our mediation hypothesis.
The effects of climate knowledge and risk assessment consistency are negative and significant as in the original model summarised in Table~\ref{Climpol435}. The results are, on the whole, robust.
\caption{\vspace{-0.35cm}\textit{\textbf{Climate change seriousness perception:} Jackknife OLS - robustness}}
% soubor Ccare435InOutb.R  Ccare535InOutbKM2.R
\label{ClimCareInOut} 
\vspace{-0.33cm}Gender = male&$-0.302$&$0.001~^{*}$&$-0.285$&$0.001~^{**}$\\
\vspace{-0.33cm}Climate knowledge\tnote{a}&$-0.187$&$<2\times10^{-8}~^{***}$&$-0.182$&$<2\times10^{-8}~^{***}$\\
 Redistribution of income:&\multirow{2}{*}{$0.297$}&\multirow{2}{*}{$1.000$}&  \multirow{2}{*}{$0.298$}&\multirow{2}{*}{$1.000$}  \\%-1
    \vspace{-0.33cm}   \hspace{0.6cm}disagree\tnote{b}&&&&\\%-1
  \vspace{-0.33cm}Redistribution of inc.: neutral\tnote{b}&$0.256$&$1.000$ &$0.263$&$1.000$\\%0
  \vspace{-0.35cm}Redistribution of income: agree\tnote{b}&$0.778$&$2\times10^{-7}~^{***}$&$0.806$&$8\times10^{-8}~^{***}$\\%1
  Redistribution of income:& \multirow{2}{*}{$0.937$}&\multirow{2}{*}{$<2\times10^{-8}~^{***}$}&\multirow{2}{*}{$0.939$}&\multirow{2}{*}{$<2\times10^{-8}~^{***}$}\\
\hspace{0.6cm}strongly agree\tnote{b}&&&\\%2
\hline\vspace{-0.33cm}
\vspace{-0.33cm}Income- predicted (mill. \textsterling~/yr.)&$2.760$&$1.000$&\multicolumn{2}{c}{\textit{Not included}}\\ %income PREDICTED!!
\vspace{-0.33cm}Income- reported (mill. \textsterling~/yr.)\tnote{c}&\multicolumn{2}{c}{\textit{Not included}}&\textit{varies}&$1.000$\\ %income PREDICTED!!
\vspace{-0.33cm}Net assets (million \textsterling)&$-0.163$&$1.000$&$-0.310$&$1.000$\\ 
\vspace{-0.33cm}People per mill. km\textsuperscript{2}-LSOA level&\multirow{1}{*}{$9.838$}&\multirow{1}{*}{$1.000$}&\multicolumn{2}{c}{\multirow{1}{*}{\textit{Not included}}}\\%ha is a symbol for hectares
  \vspace{-0.33cm}People per mill. km\textsuperscript{2}-LAD level&\multicolumn{2}{c}{\multirow{1}{*}{\textit{Not included}}}&\multirow{1}{*}{$-6.520$}&\multirow{1}{*}{$1.000$}\\%ha is a symbol for hectares
  \vspace{-0.33cm}WTP-gas and elec. tax (\textsterling~/ yr.)&$0.002$&$0.0003~^{***}$&$0.002$&$0.0005~^{***}$\\
  \vspace{-0.33cm}WTP-duty on transp. fuel (p./yr.)&$0.005$&$1.000$& $0.005$&$1.000$\\
    \vspace{-0.33cm}Climate vs. policy effects perc.&$0.356$&$<2\times10^{-8}~^{***}$&$0.359$&$<2\times10^{-8}~^{***}$\\
Social value orientation&\multirow{2}{*}{$0.003$}&\multirow{2}{*}{$1.000$}&\multirow{2}{*}{$0.003$}&\multirow{2}{*}{$1.000$}\\
    \vspace{-0.33cm}\multirow{1}{*}{Inequity aversion (categorical)}&\textit{$+$, varies}& \multirow{1}{*}{$1.000$}& \multirow{1}{*}{\textit{$+$, varies}}& \multirow{1}{*}{$1.000$}\\      
    \\ \vspace{-0.33cm}Discount rate yr. from now&$0.0003$&$1.000$&$4\times10^{-5}$&$1.000$\\  
 \vspace{-0.33cm}Discount rate yr. from now - sq.\tnote{d}&\multirow{1}{*}{$-2\times10^{-6}$}&\multirow{1}{*}{$1.000$}&\multirow{1}{*}{$-1\times10^{-6}$}&\multirow{1}{*}{$1.000$}\\
  \\  \vspace{-0.33cm}Risk aversion coefficient\tnote{e}&\multicolumn{2}{c}{\textit{Not included}}&$0.731$&$1.000$\\          
          Mean adjusted \textit{R\textsuperscript2}:&\multicolumn{2}{c}{$0.247$}&\multicolumn{2}{c}{$0.254$}\\

 \item \textit{Notes:}\hspace{0.2cm}$^{\bullet}~p<0.1$; $^{*}~p<0.05$; $^{**}~p<0.01$; $^{***}~p<0.001$
 \begin{adjustwidth}{0.9cm}{}
  \vspace{-0.3cm}
 \item[a]~Squared term of climate knowledge is insignificant in this version, hence it is not included.
  \item[b]~Degree of agreement with the following statement: 'Government should redistribute income from the better off to those who are less well off.' The base category is 'Strongly disagree'.
  \item[c]~Self reported income is only available as categorical.
  \item[d]~If squared discount rate is omitted, linear discount rate remains insignificant and the estimates of the other covariates are almost the same as those presented in this table.
  \item[e]~The risk aversion coefficient is an estimated parameter of a utility function. In this model, the median of power function is used. We also estimated varieties of this model with different risk aversion coefficients, particularly means or medians of various utility functions. These are power, log, exponential and quadratic. The risk aversion parameter is always insignificant and whether it is included or not (or which one) does not affect sign or significance level of any other parameter.
     \end{adjustwidth}    
\singlespacing  
  \end{footnotesize}
\end{tablenotes}
  \end{threeparttable} 
\par}
\caption{\vspace{-0.2cm}\textit{\textbf{Climate versus policy effects perception:} Jackknife OLS - robustness}}
% soubor Cpol435InOutb.R  Cpol535InOutbKM2.R
\label{ClimPolInOut} 
\vspace{-0.33cm}Climate knowledge\tnote{a}&$-0.127$&$8\times10^{-5}~^{***}$&$-0.128$&$0.0001~^{***}$\\
\vspace{-0.33cm}Understands inflation $=0.5$&$0.051$&$1.000$&$0.028$&$1.000$ \\
\vspace{-0.33cm}Understands inflation $=1$&$-0.219$&$1.000$&$-0.243$&$1.000$\\
  Consistent answers to risk&\multirow{2}{*}{$-0.310$}&\multirow{2}{*}{$0.019~^{*}$}&\multirow{2}{*}{$-0.305$}&\multirow{2}{*}{$0.038~^{*}$}\\
\vspace{-0.33cm}Income- predicted (mill. \textsterling~/yr.)&$2.446$&$1.000$&\multicolumn{2}{c}{\textit{Not included}}\\ %income PREDICTED!!
\vspace{-0.33cm}Net assets (million \textsterling)&$-0.070$&$1.000$&$0.027$&$1.000$\\ 
\vspace{-0.33cm}People per mill. km\textsuperscript{2}-LSOA level&\multirow{1}{*}{$-16.683$}&\multirow{1}{*}{$1.000$}&\multicolumn{2}{c}{\multirow{1}{*}{\textit{Not included}}}\\%ha is a symbol for hectares
\vspace{-0.33cm}People per mill. km\textsuperscript{2}-LAD level&\multicolumn{2}{c}{\multirow{1}{*}{\textit{Not included}}}&\multirow{1}{*}{$15.548$}&\multirow{1}{*}{$1.000$}\\%ha is a symbol for hectares
  \vspace{-0.33cm}WTP- gas and electric. tax (\textsterling~/ yr.)&$0.002$&$9\times10^{-5}~^{***}$&$0.002$&$9\times10^{-5}~^{***}$\\
  \vspace{-0.33cm}WTP-duty on transport fuel (p./yr.)&$0.011$&$9\times10^{-5}~^{***}$& $0.010$&$0.001~^{**}$\\
    \vspace{-0.33cm}Climate seriousness perception&$0.382$&$\small{<}2\times10^{-8}~^{***}$&$0.387$&$\small{<}2\times10^{-8}~^{***}$\\
Social value orientation&\multirow{2}{*}{$0.006$}&\multirow{2}{*}{$0.396$}&\multirow{2}{*}{$0.005$}&\multirow{2}{*}{$0.726$}\\
    \\ \vspace{-0.33cm}Discount rate yr. from now&$-0.001$&$1.000$&$-0.001$&$1.000$\\  
 \vspace{-0.33cm}Discount rate yr. from now - sq.\tnote{c}&\multirow{1}{*}{$2\times10^{-6}$}&\multirow{1}{*}{$1.000$}&\multirow{1}{*}{$2\times10^{-6}$}&\multirow{1}{*}{$1.000$}\\
  \\  \vspace{-0.33cm}Risk aversion coefficient\tnote{d}&\multicolumn{2}{c}{\textit{Not included}}&$-0.523$&$1.000$\\          
  \vspace{-0.35cm}Redistribution of income (categ.)\tnote{e}&\textit{$+$,varies}&$1.000$&\textit{$+$,varies}&$1.000$\\%1
          Mean adjusted \textit{R\textsuperscript2}:&\multicolumn{2}{c}{$0.254$}&\multicolumn{2}{c}{$0.257$}\\
\item[c]~If squared discount rate is omitted, linear discount rate remains insignificant and the estimates of the other covariates are almost the same as those presented in this table.
\item[d]~The risk aversion coefficient is an estimated parameter of a utility function. In this model, the mean of power function is used. We also estimated varieties of this model with different risk aversion coefficients, particularly means or medians of various utility functions. These are power, log, exponential and quadratic. The risk aversion parameter is always insignificant and whether it is included or not (or which one) does not affect sign or significance level of any other parameter. 
\item[e]~A degree of agreement with the statement: 'Government should redistribute income from the better off to those who are less well off.' Included to test for significance of political opinions.

\subsection{Willingness to pay for climate change mitigation}\label{RobWTP}

In this section we verify robustness of the models with dependent variable  WTP for climate change mitigation. Table~\ref{GasInOut} summarises estimates of two varieties of the models specified in Section~\ref{ResWTP} with additional behavioural variables, climate change variables and other potential confounders discussed at the beginning of Section~\ref{Robust}. The estimates of the predictors which were originally selected by the multisplit lasso (in the first $11$ rows of Table~\ref{GasInOut}) are qualitatively the same as those of the models in Table~\ref{Gas435cp}. The only exception is the dummy variable for scoring $0.5$ on understanding of compound interest as its estimate is negative in Table~\ref{Gas435cp} while it is positive in both models in Table~\ref{GasInOut}. However, the estimate of this dummy variable is insignificant in each of these models so the difference in signs does not imply that the estimates are not robust.

Similarly as in the case of the robustness model for climate knowledge (Table~\ref{ClimKnowInOut}) and the robustness models for climate change risk perception (Tables~\ref{ClimCareInOut} and~\ref{ClimPolInOut}) the climate change variables are significant (with the exemption of climate knowledge) while the other potential confounders and behavioural variables in the second half of Table~\ref{GasInOut} are insignificant. An exemption is predicted income, which has a significant impact on WTP.\footnote{Interestingly, the categorical income recorded in the survey \citep{SurveyUK} is not significant. We suspect that it can be due to inaccuracy of the income variable recorded in the survey as relatively big number of participants are students and it is not clear if they stated their own income or income of their parents. The possible inaccuracy of the income measure is one of the reasons why we also use the alternative predicted income.} The significance of income can be explained by its diminishing marginal utility. For people with higher income, the utility of amount of money paid as climate tax is lower than for people with lower income. Therefore, preferred tax rates are higher for higher income groups. Whether or not income or the other additional explanatory variables are included does not have any significant impact on estimates of the predictors in Table~\ref{GasInOut} which were chosen by the means of the multisplit lasso in Section~\ref{ResWTP}.

Pride may have played role in the strong significance of current tax rates estimates. As explained in Section~\ref{ClimateVars}, the respondents were informed about the correct tax rates after they gave their estimates and before they were asked about their preferences regarding the climate policies.  It is possible that respondents tended to give preferred tax rates which were close to their estimate of the current tax rates feeling that their estimate should be the preferred one.

{\centering
\begin{threeparttable}
\singlespacing
\caption{\textit{\textbf{\small{WTP climate - gas and electricity tax:}} Jackknife OLS - robustness}}
% soubor Gas435InOut3.R a %Gas535InOutKm2b.R
% % soubor Gas435InOut5.R a %Gas535InOutKm2c.R jeste to odhaduju znovu a davam tam ty kategoricky jako scale, jen abych vedela jestli muzu napsat negative/positive correlation

\label{GasInOut} 
\vspace{-1cm}
\vspace{-0.8cm}
  \multicolumn{1}{l}{}&\multicolumn{2}{c}{\textbf{Model} $\boldsymbol{1}$}% Gas435InOut3.R
  &\multicolumn{2}{c}{\textbf{Model} $\boldsymbol{2}$}\\%Gas535InOutKm2b.R
 \multicolumn{1}{l}{\textbf{Variable}} & \multicolumn{1}{c}{\textbf{coef.}}& \multicolumn{1}{c}{\textbf{adj. \textit{p}-value}}& \multicolumn{1}{c}{\textbf{coef.}} &  \multicolumn{1}{c}{\textbf{adj. \textit{p}-value}} \\
\hline  \vspace{-0.345cm}
\vspace{-0.345cm}Age (categorical)\tnote{a}&\multicolumn{2}{c}{\textit{negative cor.~}$^{***}$}&\multicolumn{2}{c}{\textit{negative cor.~}$^{***}$}\\
\vspace{-0.345cm}Climate vs. policy effects perc.&$6.654$&$<2\times10^{-8}~^{***}$&$6.534$&$<2\times10^{-8}~^{***}$\\
  \vspace{-0.345cm}Inequity aversion (categorical)\tnote{a}&\multicolumn{2}{c}{\textit{negative cor.~}$^{**}$}&\multicolumn{2}{c}{\textit{negative cor.~}$^{**}$}\\
 Equal intergenerational&\multirow{2}{*}{$18.843$}&\multirow{2}{*}{${0.004}~^{**}$}&\multirow{2}{*}{$19.646$}&\multirow{2}{*}{${0.004}~^{**}$}\\
\vspace{-0.345cm}\hspace{0.6cm}allocation of resources $(0/1)$&\\
\vspace{-0.345cm}Understands comp. interest $=0.5$&$1.276$&$1.000$&$3.870$&$1.000$ \\
\vspace{-0.345cm}Understands comp. interest $=1$&$-34.032$&$0.0003~^{***}$&$-32.084$&$0.001~^{***}$\\
\vspace{-0.345cm}Understands inflation$=0.5$&$-12.364$&$1.000$&$-11.779$&$1.000$\\
\vspace{-0.345cm}Understands inflation$=1$&$-31.737$&$<2\times10^{-8}~^{***}$&$-29.101$&$<2\times10^{-8}~^{***}$\\
Consistent answers to risk $(0/1)$&\multirow{1}{*}{$-28.046$}&\multirow{1}{*}{$<2\times10^{-8}~^{***}$}&\multirow{1}{*}{$-27.714$}&\multirow{1}{*}{$<2\times10^{-8}~^{***}$}\\
\hline \vspace{-0.345cm}\\
\vspace{-0.345cm}Income- predicted (thousand \textsterling/yr.)&$0.703$&$3\times10^{-5}~^{***}$&\multicolumn{2}{c}{\textit{Not included}}\\ %income PREDICTED!!
\vspace{-0.345cm}Income- reported (mill. \textsterling/yr.)\tnote{a}&\multicolumn{2}{c}{\textit{Not included}}&$+$,\textit{varies}&$1.000$\\ %income PREDICTED!!
\vspace{-0.345cm}Net assets (million \textsterling)&$18.033$&$0.133$&$20.072$&$0.151$\\ 
\vspace{-0.345cm}People per mill. km\textsuperscript{2}-LSOA level&\multirow{1}{*}{$768.974$}&\multirow{1}{*}{$1.000$}&\multicolumn{2}{c}{\multirow{1}{*}{\textit{Not included}}}\\%ha is a symbol for hectares
\vspace{-0.345cm}People per mill. km\textsuperscript{2}-LAD level&\multicolumn{2}{c}{\multirow{1}{*}{\textit{Not included}}}&\multirow{1}{*}{$594.369$}&\multirow{1}{*}{$1.000$}%ha is a symbol for hectares
  \\  \\
\vspace{-0.345cm}Climate knowledge&$0.020$&$1.000$&$0.556$&$1.000$\\
  \vspace{-0.345cm}How much is tax gas and el.\small{(\textsterling~/yr.)}&$0.252$&$\small{<}2\times10^{-8}~^{***}$&$0.251$&$\small{<}2\times10^{-8}~^{***}$\\
    \vspace{-0.345cm}Climate seriousness perception&$7.158$&$\small{<2\times10^{-8}}~^{***}$&$7.282$&$\small{<}2\times10^{-8}~^{***}$\\
\vspace{-0.345cm}Social val. orientation (ring meas.)&\multirow{1}{*}{$0.048$}&\multirow{1}{*}{$1.000$}&\multirow{1}{*}{$0.009$}&\multirow{1}{*}{$1.000$}\\ % ring measure> ref working paper dolton tol     
    \\ \vspace{-0.34cm}Discount rate yr. from now&$-0.078$&$1.000$&$-0.084$&$1.000$\\  
 \vspace{-0.345cm}Discount rate yr. from now - sq.\tnote{b}&\multirow{1}{*}{$0.0002$}&\multirow{1}{*}{$0.992$}&\multirow{1}{*}{$0.0002$}&\multirow{1}{*}{$0.908$}\\
  \\  \vspace{-0.345cm}Risk aversion coefficient\tnote{c}&\multicolumn{2}{c}{\textit{Not included}}&$-0.261$&$1.000$\\          
  \vspace{-0.35cm}Redistribution of income (cat.)\tnote{d}&\textit{varies}&$1.000$&\textit{varies}&$1.000$\\
Mean adjusted \textit{R\textsuperscript2}:&\multicolumn{2}{c}{$0.370$}&\multicolumn{2}{c}{$0.364$}\\
 \item \textit{Notes:}\hspace{0.2cm}$^{\bullet}~p<0.1$; $^{*}~p<0.05$; $^{**}~p<0.01$; $^{***}~p<0.001$;\hspace{0.4cm} 
  \vspace{-0.4cm}\large{\textsuperscript{\textbf{a}}}~\footnotesize{Age and reported income only available}\\ \begin{adjustwidth}{0.7cm}{} \footnotesize{as  categorical. Inequity av. treated as categorical (see Sec.~\ref{Method})\hspace{0.4cm}} 
  \large{\textsuperscript{\textbf{b}}}~\footnotesize{If squared discount rate is omitted, linear discount rate remains insignificant and the estimates of the other covariates are almost the same as those presented in this table.\hspace{0.4cm}} 
  \large{\textsuperscript{\textbf{c}}}~\footnotesize{The risk aversion coefficient is an estimated parameter of a utility function. In this model, the mean of power function is used. We also estimated varieties of this model with different risk aversion coefficients, particularly means or medians of power, log, exponential or quadratic utility function. The risk aversion parameter is always insignificant and whether it is included or not (or which one) does not affect sign or significance level of any other parameter.\hspace{0.4cm}}\normalsize{\textsuperscript{\textbf{d}}}~\footnotesize{A degree of agreement with the statement: 'Government should redistribute income from the better off to those who are less well off.'}

As another robustness test we use preferred tax rates on transport fuel as a measure of WTP. The estimates are summarised in Table~\ref{FuelInOut}. Model~$1$ in Table~\ref{FuelInOut} only includes explanatory variables which were chosen for WTP using the lasso in Section~\ref{ResWTP}. Model~$2$ in Table~\ref{FuelInOut} also includes climate variables, behavioural variables and additional potential confounders to test their significance and to examine whether or not their inclusion changes signs or significance levels of the main predictors. Comparing Model~$1$ in Table~\ref{FuelInOut} with the estimates of the models in Table~\ref{Gas435cp} (Section~\ref{ResWTP}), we can see that the signs and significance levels of the coefficients are the same in these two models. Also their magnitude is comparable considering the different scales of the two dependent variables. Regarding Model~$2$ in Table~\ref{FuelInOut}, we can see that inclusion of the additional explanatory variables does not change signs or significance levels of the main predictors (the variables in the first $11$ rows of Table~\ref{FuelInOut}). An exemption is dummy variable for scoring $0.5$ on understanding of inflation as in Model~$1$ the coefficient is negative while in Model~$2$ it is positive. However, this change is unremarkable as these coefficients of understanding of inflation are insignificant in both models. The additional explanatory variables in Model~$2$ in Table~\ref{FuelInOut} are insignificant except of the estimate of current fuel duty and climate seriousness perception. The signs of all the additional variables are the same as their signs in the model for WTP on gas and electricity in Table~\ref{GasInOut}. Interestingly, income does not have any significant impact on preferred fuel duty although its impact on gas and electricity tax is significant. Our explanation is that individuals with lower income exhibit lower WTP through gas and electricity tax, but they are less likely to own a car (thus they are less likely to be eligible for paying transport fuel duty). Thus, when asked about their preferred rates on fuel duty, they actually impose the duty on those owning a car rather than on themselves. It is understandable that preferred tax rates imposed on others are higher than preferred tax rates paid by ourselves. Hence, people with lower income may exhibit higher preferred fuel duty as they impose it on others rather than on yourself. This may offset the significant positive impact of income, which we detected in the model for gas and electricity tax. Even lower income groups are eligible for gas and electricity tax, therefore the positive influence of income is significant as it is not offset by the fact that lower income groups impose the tax on others rather than on themselves.

We can conclude that our models are reasonable robust.
\caption{\textit{\textbf{\vspace{-0.6cm} WTP climate - duty on transport fuel:} Jackknife OLS}}
% soubor FuelGas4cp.R a %.FuelGas4bInOut.R % soubor FuelGas5cp.R  %.FuelGas4bInOut4.R
\label{FuelInOut} 
\vspace{-0.8cm}
  \multicolumn{1}{l}{}&\multicolumn{2}{c}{\textbf{Model} $\boldsymbol{1}$}% FuelGas4cp.R
  &\multicolumn{2}{c}{\textbf{Model} $\boldsymbol{2}$}\\%.FuelGas4bInOut.R
 \multicolumn{1}{l}{\textbf{Variable}} & \multicolumn{1}{c}{\textbf{coef.}}& \multicolumn{1}{c}{\textbf{adj. \textit{p}-val.}}& \multicolumn{1}{c}{\textbf{coef.}} &  \multicolumn{1}{c}{\textbf{adj. \textit{p}-val.}} \\
\hline  \vspace{-0.32cm} 
\vspace{-0.32cm}Age (categorical)\tnote{a}&\multicolumn{2}{c}{\textit{negative cor.~}$^{***}$}&\multicolumn{2}{c}{\textit{negative cor.~}$^{***}$}\\
\vspace{-0.32cm}Climate vs. policy effects perception&$2.192$&$<2\times10^{-8}~^{***}$&$1.494$&$<2\times10^{-8}~^{***}$\\
  \vspace{-0.32cm}Inequity aversion (categorical)\tnote{a}&\multicolumn{2}{c}{\textit{negative cor.~}$^{**}$}&\multicolumn{2}{c}{\textit{negative cor.~}$^{**}$}\\
 Equal intergenerational&\multirow{2}{*}{$4.461$}&\multirow{2}{*}{${0.002}~^{**}$}&\multirow{2}{*}{$4.824$}&\multirow{2}{*}{${0.0004}~^{***}$}\\
\vspace{-0.32cm}\hspace{0.6cm}allocation of resources $(0/1)$&\\
\vspace{-0.32cm}Understands compound interest$=0.5$&$1.703$&$1.000$&$1.818$&$1.000$ \\
\vspace{-0.32cm}Understands compound interest$=1$&$-7.363$&$0.001~^{***}$&$-7.091$&$0.0008~^{***}$\\
\vspace{-0.32cm}Understands inflation$=0.5$&$-0.602$&$1.000$&$0.135$&$1.000$\\
\vspace{-0.32cm}Understands inflation$=1$&$-7.458$&$<2\times10^{-8}~^{***}$&$-5.834$&$4\times10^{-7}~^{***}$\\
  Consistent answers to risk&\multirow{2}{*}{$-6.294$}&\multirow{2}{*}{$<2\times10^{-8}~^{***}$}&\multirow{2}{*}{$-5.591$}&\multirow{2}{*}{$<2\times10^{-8}~^{***}$}\\
\hline \vspace{-0.3cm}\\
\vspace{-0.32cm}Income - predicted (thousands \textsterling~/yr.)&\multicolumn{2}{c}{\textit{Not included}}&$88.788$&$0.344$ \\ %income PREDICTED!!
\vspace{-0.32cm}Net assets (million pounds \textsterling)&\multicolumn{2}{c}{\textit{Not included}}&$3.168$&$0.936$\\ 
